---
output:
  rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

  library(magrittr)

```

# `envEcosystems`: an R package of objects and tools to create ecosystem descriptions

<!-- badges: start -->
<!-- badges: end -->

The goal of `envEcosystems` is to provide tools and objects for creating ecosystem descriptions based on outputs from other `env`Packages.

## Installation

`envEcosystems` is not on [CRAN](https://CRAN.R-project.org).

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Acanthiza/envEcosystems")
```

Load `envEcosystems`

```{r}
library("envEcosystems")
```

## Convert between cover value systems

`lucover` provides a lookup table from modified Braun-Blanquet cover codes to various numeric cover values.

```{r}

  lucover

```

## What else is in `envEcosystems`

The following functions and data sets are provided in `envEcosystems`. See https://acanthiza.github.io/envEcosystems/ for more examples.

```{r, echo = FALSE, warning = FALSE}

  get_name_title <- function(text) {
    
    tibble::enframe(text
                    , name = NULL
                    , value = "description"
                    ) %>%
      dplyr::filter(grepl("title", description)) %>%
      dplyr::mutate(description = gsub("\\\\|title", "", description)
                    , description = gsub("^\\{|\\}$", "", description)
                    )
    
  }

  manuals <- fs::dir_info("man") %>%
    dplyr::select(path) %>%
    dplyr::filter(grepl("Rd$", path)
                  , !grepl("pipe", path)
                  ) %>%
    dplyr::mutate(object = gsub("man\\/|\\.Rd","",path)
                  , class = purrr::map_chr(object, ~envFunc::vec_to_sentence(class(get(.))))
                  , text = purrr::map(path, readLines)
                  , text = purrr::map(text, get_name_title)
                  , object = paste0("["
                                  , object
                                  , dplyr::if_else(class == "function"
                                                   , "()"
                                                   , ""
                                                   )
                                  , "]"
                                  )
                  ) %>%
    tidyr::unnest(cols = c(text))

  knitr::kable(manuals[,2:4])

```




